\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-04-17 doc/paper.tex
update the example model file
The calculation of the Yukawa couplings must defined explicitely.

LowScaleInput = {
   {vd, 2 MZDRbar / Sqrt[GUTNormalization[g1]^2 g1^2 + g2^2] Cos[ArcTan[TanBeta]]},
   {vu, 2 MZDRbar / Sqrt[GUTNormalization[g1]^2 g1^2 + g2^2] Sin[ArcTan[TanBeta]]}
};

InitialGuessAtLowScale = {
   {vd, SM[vev] Cos[ArcTan[TanBeta]]},
   {vu, SM[vev] Sin[ArcTan[TanBeta]]}
};

@@

The list of parameter settings can contain as elements any of the
following:
%
\begin{itemize}
\item Two-component lists of the form \code{\{parameter, value\}},
  which indicates that the \code{parameter} is set to \code{value} at
  the defined scale.  If the \code{value} should be read from the SLHA
  input file, it must be written as \code{LHInput[value]}.  Example:
  %
  \begin{lstlisting}
SUSYScaleInput = {
   {mHd2, m0^2},
   {mHu2, LHInput[mHu2]}
};
  \end{lstlisting}
  %
  In this example the parameter \code{mHd2} is set to the value of
  \code{m0^2}, and \code{mHu2} is set to the value given in the SLHA
  input file in block \code{MSOFTIN}, entry 22.  The SLHA block names
  and keys for the MSSM and NMSSM are defined in SARAH's
  \code{parameters.m} file, see the SARAH manual or
  \cite{Staub:2010jh}.

@@

Finally the user can set an initial guess for the model parameters at
the low- and high-scale using the variables
\code{InitialGuessAtLowScale} and \code{InitialGuessAtHighScale},
respectively.  Note, that the gauge and Yukawa couplings will be
guessed automatically at the low-scale from the known Standard Model
parameters.

>>>>

LowScaleInput = {
   {Yu, Automatic},
   {Yd, Automatic},
   {Ye, Automatic},
   {vd, 2 MZDRbar / Sqrt[GUTNormalization[g1]^2 g1^2 + g2^2] Cos[ArcTan[TanBeta]]},
   {vu, 2 MZDRbar / Sqrt[GUTNormalization[g1]^2 g1^2 + g2^2] Sin[ArcTan[TanBeta]]}
};

InitialGuessAtLowScale = {
   {vd, SM[vev] Cos[ArcTan[TanBeta]]},
   {vu, SM[vev] Sin[ArcTan[TanBeta]]},
   {Yu, Automatic},
   {Yd, Automatic},
   {Ye, Automatic}
};

@@

The list of parameter settings can contain as elements any of the
following:
%
\begin{itemize}
\item Two-component lists of the form \code{\{parameter, value\}},
  which indicates that the \code{parameter} is set to \code{value} at
  the defined scale.  If the \code{value} should be read from the SLHA
  input file, it must be written as \code{LHInput[value]}.  Example:
  %
  \begin{lstlisting}
SUSYScaleInput = {
   {mHd2, m0^2},
   {mHu2, LHInput[mHu2]}
};
  \end{lstlisting}
  %
  In this example the parameter \code{mHd2} is set to the value of
  \code{m0^2}, and \code{mHu2} is set to the value given in the SLHA
  input file in block \code{MSOFTIN}, entry 22.  The SLHA block names
  and keys for the MSSM and NMSSM are defined in SARAH's
  \code{parameters.m} file, see the SARAH manual or
  \cite{Staub:2010jh}.  The Standard Model Yukawa couplings \code{Yu},
  \code{Yd}, \code{Ye} can be calculated automatically from the known
  Standard Model quark and lepton masses, see
  Section~\ref{sec:calculation-of-yukawa-couplings}.  To enable the
  automatic calculation, \code{value} must be set to \code{Automatic},
  see the example above.

@@

Finally the user can set an initial guess for the model parameters at
the low- and high-scale using the variables
\code{InitialGuessAtLowScale} and \code{InitialGuessAtHighScale},
respectively.  Note, that the gauge couplings will be guessed
automatically at the low-scale from the known Standard Model
parameters, see Section~\ref{sec:calculation-of-gauge-couplings}.
